Kindly Bent to Free Us

### 2019-07-11 kindly/infer/infer.tex
beginning of explanation constraint solving

Before presenting our constraint solving algorithm,
we place ourselves in a more general context where kinds are either variables
or constants belonging to a total bounded lattice $(\mathcal L, \lk_\Lat)$ ie.,
a lattice which admits a total order and upper and lower bounds ($l^\top$ and $l^\bot$).
We note lattice elements $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
the greatest lower bound (resp. least upper bound) in $\mathcal L$.
The lattice used in \lang which was presented
in \cref{sdtyping} is a total bounded lattice with
$l^\top = \klin_\infty$ and $l^\bot = \kun_0$.
%
Let $\CL$ the set of constraints in such arbitrary lattice $mathcal L$.
The full grammar of constraints is shown in \cref{grammar:constraint}.
Constraints are made of kind inequalities, conjunctions and
projections, as shown previously, along with type unification
constraints. Since types might contain kinds (for instance, on the arrows),
type unification is oriented and noted $\leq$.
For simplicity, we consider all type constructors
invariant in their parameters
and define $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.

@@

\TODO{Add example}

Our algorithm is complete, computes principal normal forms,
and already simplifies constraints significantly
(notably thanks to steps 6, 7 and 8).
It can be easily extended with further simplification phases.
In particular, our implementation and all the signatures presented in
\cref{motivation} use a variance-based simplification
where all covariant (resp. contravariant) variables are replaced by their
lower (resp. upper) bounds.
Remarkably, all the simplification mechanisms presented
here (including the variance-based one) are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.
%
We now show that this algorithms is well-behaved with respect to entailment
and computes unique normal forms.

>>>>

We define the constraint solver in terms of an arbitrary bounded
lattice $(\mathcal L, \lk_\Lat)$, i.e., 
a lattice which has a minimal and a maximal element ($l^\top$ and $l^\bot$).
We write lattice elements as $l$ and $\glb_i l_i$ (resp. $\lub_i l_i$)
for the greatest lower bound (resp. least upper bound) in $\mathcal L$.
The lattice for \lang (see \cref{sdtyping}) is a bounded lattice with
$l^\top = \klin_\infty$ and $l^\bot = \kun_0$.
%
Let $\CL$ be the set of constraints in such a lattice $\mathcal L$.
The full grammar of constraints is shown in \cref{grammar:constraint}.
Constraints are made of kind inequalities, conjunctions and
projections, as shown previously, along with type unification
constraints. Since types might contain kinds (for instance, on the arrows),
type unification is oriented and noted $\leq$.
For simplicity, we consider all type constructors
invariant in their parameters
and define $\Ceq{\tau}{\tau'}$ as $\Cleq{\tau}{\tau'} \wedge \Cleq{\tau'}{\tau}$.

@@

An example of this algorithm in action is shown in \cref{solving:example}.
Our algorithm is complete, computes principal normal forms,
and already simplifies constraints significantly
(notably thanks to steps 6, 7 and 8).
It can be easily extended with further simplification phases.
In particular, our implementation and all the signatures presented in
\cref{motivation} use a variance-based simplification
where all covariant (resp. contravariant) variables are replaced by their
lower (resp. upper) bounds.
Remarkably, all the simplification mechanisms presented
here (including the variance-based one) are complete.
It is also possible to add ``best-effort'' simplification
rules which help reduce the size of inferred signatures even further
\citep{DBLP:conf/aplas/Simonet03}.
%
We now show that this algorithms is well-behaved with respect to entailment
and computes unique normal forms.
